Doing Better Than UCT: \\ Rational Monte Carlo Sampling in Trees

### 2011-08-17 paper/rmcts/paper.tex
vct with uqb

Another improved allocation scheme (UQB) for minimizing the simple
regret is obtained by substituting $\sqrt{\cdot}$ instead of $\log(\cdot)$ into
the formula for UCB and has a superpolynomial convergence rate
(see Appendix~\ref{app:derivations-asym-ucb}).

@@

VOI of a rollout can be computed when the sample distribution of an
action is known up to the parameters, such as the normal distribution
with an unknown mean and/or variance. Alternatively, the value of
information can be estimated from the set of samples, and the need to
assume a particular shape of the distribution is be lifted. In one
realization of the latter approach the VOI of performing an action is
estimated as the value of perfect information learned from the outcome
of earlier samples of the action divided by the number of
samples. Early experiments with this approach showed the best
performance for sets of Bernoulli arms, and even a more prominent
improvement for mixed arms (e.g. Bernoulli, triangularly distributed,
and fixed arms) (Figure~\ref{fig:flat-trilevel-vct}).  Sample-based
VOI estimation requires keeping more information than an algorithm
based only on the sample mean, but the overhead is small and justifies
the improvement.

>>>>

Another improved allocation scheme for minimizing the simple regret,
called \textbf{UQB} here, is obtained by substituting $\sqrt{\cdot}$
instead of $\log(\cdot)$ into the formula for UCB and has a
superpolynomial convergence rate (see
Appendix~\ref{app:derivations-asym-ucb}).

@@

VOI of a rollout can be computed when the sample distribution of an
action is known up to the parameters, such as the normal distribution
with an unknown mean and/or variance. Alternatively, the value of
information can be estimated from the set of samples, and the need to
assume a particular shape of the distribution is be lifted. In one
realization of the latter approach the VOI of performing an action is
estimated as the value of perfect information learned from the outcome
of earlier samples of the action divided by the number of
samples. Early experiments with this approach showed the best
performance for sets of Bernoulli arms, and even a more prominent
improvement for mixed arms (e.g. Bernoulli, triangularly distributed,
and fixed arms) (Figure~\ref{fig:flat-trilevel-vct}):
\textbf{VCT}, the algorithm which selects an action with the maximum VOI estimate on
the first step exhibits lower average regret than other algorithms.
Sample-based VOI estimation requires keeping more information than an
algorithm based only on the sample mean, but the overhead is small and justifies
the improvement.
